---
title: "Replication 3"
author: "Enxhi Buxheli"
date: "3/5/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# NOTE: Comments will be contrary to tidyverse styling as I do not include an
# extra line to describe code chunk below comments

# Attaching libraries as in slavery-jop-replication.R
library(foreign)
library(plyr)
library(reshape)
library(sandwich)
library(maps)
library(stargazer)
library(AER)
library(Formula)
library(lme4)
library(cem)
library(latticeExtra)
library(stringr)
library(gt)


# Not quite sure what this panel-utils.R file does, looks like it's a function
# file along with some formatting stuff such as colors added
source("dataverse_files/panel-utils.R")

# Adding in more color formatting (they really like colors)
dodgerblue.30 <- rgb(30, 144, 255, 76.5, max = 255)
indianred.30 <- rgb(205, 92, 92, 76.5, max = 255)
indianred.75 <- rgb(205, 92, 92, 191, max = 255)
```

## R Markdown
```{r state_cleanup, results = 'asis'}
# Loading in the state FIPS encoding data
data(state.fips)

# Cleaning up the fips data to include only the relevant columns a deduping states
state.fips <- unique(state.fips[,c("fips","abb")])
state.fips$abb <- as.character(state.fips$abb)
state.fips <- rbind(state.fips, c(2, "AK"))
state.fips <- rbind(state.fips, c(15, "HI"))
rownames(state.fips) <- state.fips$abb

# Creating a new dataset called fips.state from our cleaned state.fips set
fips.state <- state.fips
rownames(fips.state) <- fips.state$fips
data(county.fips)
```

# Adding additional functions
```{r functions}
## The below is not the intended link, but I'm assuming that it's supposed to
## show that the clustering methods used in developing this standard error model
## are legitimate and in a published work by a professor from Stockholm
## University
# http://people.su.se/~ma/clustering.pdf
robust.se <- function(fm, clvar){
    # R-codes (www.r-project.org) for computing
    # clustered-standard errors. Mahmood Arai, Jan 26, 2008.
    # The arguments of the function are:
    # fitted model, cluster1 and cluster2
    # You need to install libraries `sandwich' and `lmtest'
  library(sandwich)
  library(lmtest)
  
  x <- eval(fm$call$data, envir = parent.frame())
  if ("polr" %in% class(fm)) {
    require(MASS)
    cluster <- x[rownames(predict(fm, type = "probs")), clvar]
  } 
  else {
    cluster <- x[names(predict(fm)), clvar]
  }
  M <- length(unique(cluster))
  N <- length(cluster)
  K <- dim(vcov(fm))[1]
  dfc <- (M/(M-1))*((N-1)/(N-K))
  uj  <- apply(estfun(fm),2, function(x) tapply(x, cluster, sum));
  vcovCL <- dfc*sandwich(fm, meat=crossprod(uj)/N)
  coeftest(fm, vcovCL)
}

# Function to add checkmark to a row (short for checkmark row)
ch.row <- function(name, yesno) {
    c(name, ifelse(yesno, "$\\checkmark$", ""))
}
```

# Reading in the data
```{r readcsv, cache = TRUE}
# Consider changing to read_csv
# The below reads in all of csv files
countydata <- read.csv("dataverse_files/abs-jop-countydata.csv", stringsAsFactors = FALSE)
wh.counties <- read.csv("dataverse_files/abs-jop-cces-white-countydata.csv", stringsAsFactors = FALSE)

# CCES data
cces.comb <- read.csv("dataverse_files/abs-jop-cces-ind.csv", stringsAsFactors = FALSE)

# ANES data
nes.counties <- read.csv("dataverse_files/abs-jop-nes-white-countydata.csv", stringsAsFactors = FALSE)
nes.comb <- read.csv("dataverse_files/abs-jop-nes-ind.csv", stringsAsFactors = FALSE)
```

# Cleaning up the data
```{r cleanup}
# List of slavery states from the south 
st.list <- c("AL", "AR", "GA", "FL", "KY", "LA", "MS", "MO", "NC", "SC", "TN", "TX", "VA","WV")

## CCES (Cooperative Congressional Election Study) Data Results
# Multiplying by 1 makes the boolean for if the person is in the south go from
# TRUE/FALSE to being 1/0
cces.comb$abs.sample   <- 1 * (cces.comb$state.abb   %in% st.list)
wh.counties$abs.sample <- 1 * (wh.counties$state.abb %in% st.list)
countydata$abs.sample  <- 1 * (countydata$state.abb  %in% st.list)

# Tractors per county acre growth from 1930 to 1940
wh.counties$tractor.growth <- (wh.counties$tractors40 - wh.counties$tractors30)

# Factorizing the income brackets in ascending order
cces.comb$inc.cat <- factor(cces.comb$inc.cat, levels = c("<20k", "20-50k", "50-100k", "100-150k", "150k+"))

# Creating racial groupings for the cces data
whites  <- cces.comb[which(cces.comb$white  == 1),]
blacks  <- cces.comb[which(cces.comb$black  == 1),]
latinos <- cces.comb[which(cces.comb$latino == 1),]
others  <- cces.comb[which(cces.comb$white  != 1 & cces.comb$black != 1 & cces.comb$latino != 1),]

## Individual-level data
# Subsetting to only include southerners as determined by the boolean above
# Also grouping by the same groups as above where s.GROUP is just an indicator
# that the grouping is of southerners.
southerners <- subset(cces.comb, abs.sample == 1)
s.whites    <- subset(whites,    abs.sample == 1)
s.blacks    <- subset(blacks,    abs.sample == 1)
s.latinos   <- subset(latinos,   abs.sample == 1)
s.whites$state.abb  <- factor(s.whites$state.abb)
s.blacks$state.abb  <- factor(s.blacks$state.abb)
s.latinos$state.abb <- factor(s.latinos$state.abb)

## County-level data
# Creating dataset of all the southern and cleaning it up
south.counties <- subset(wh.counties, abs.sample == 1)
south.counties$state.abb <- factor(south.counties$state.abb)
south.counties <- south.counties[order(as.numeric(south.counties$fips)),]


## ANES (American National Election Survey) Data Results
# Creating a boolean for if states are southern states and subsetting the results
nes.counties$abs.sample <- 1 * (nes.counties$state.abb %in% st.list)
nes.comb$abs.sample <- 1 * (nes.comb$state.abb %in% st.list)
nes.whites <- nes.comb[which(nes.comb$white == 1),]
nes.blacks <- nes.comb[which(nes.comb$black == 1),]

## Individual-level analysis
# Subsetting to only include southerners as determined by the boolean above
# Also grouping by the same groups as above where ns.GROUP is just an indicator
# that the grouping is of southerners from the ANES dataset.
ns.whites <- subset(nes.whites, abs.sample == 1)
ns.blacks <- subset(nes.blacks, abs.sample == 1)
ns.whites$state.abb <- factor(ns.whites$state.abb)
ns.blacks$state.abb <- factor(ns.blacks$state.abb)
```

# Loading in some formulas
```{r formulas, results = 'asis'}
# Creating some formulas to be used in later linear regressions
# Formula for looking at all the 1860 Census data
base1860.form <- formula(. ~ pslave1860 + log(coarea00) + latitude + I(latitude^2) + longitude + I(longitude^2)+ rugged  + land.ineq1860 + sfarmprop1860 + log(totpop1860) + log(fvalpac1860) + log(acimp1860) + fbprop1860  + rail1860 + water1860 + state.abb)

# Formula for looking at the individual 1860 Census data
ind.form <- formula(. ~ pslave1860   + log(coarea00) + latitude + I(latitude^2) + longitude + I(longitude^2) + rugged + land.ineq1860 + sfarmprop1860 + log(totpop1860) + log(fvalpac1860) + log(acimp1860) + fbprop1860 + rail1860 + water1860 + as.factor(educ) +  inc.cat +religion + female + age + state.abb*as.factor(year))

# Formula for looking at the individual interative in the 1860 Census data
ind.int.form <- formula(. ~ pslave1860   + log(coarea00) + latitude + I(latitude^2) + longitude + I(longitude^2) + rugged + land.ineq1860 + sfarmprop1860 + log(totpop1860) + log(fvalpac1860) + log(acimp1860) + fbprop1860 + rail1860 + water1860 + as.factor(educ)*pslave1860 + inc.cat*pslave1860 + religion*pslave1860 + female*pslave1860 + age*pslave1860  + state.abb*as.factor(year))

# Adding in a formula for the context (year) in which the data was collected
context.form <- formula(. ~ pslave1860   + log(coarea00) + latitude + I(latitude^2) + longitude + I(longitude^2) + rugged + land.ineq1860 + sfarmprop1860 + log(totpop1860) + log(fvalpac1860) + log(acimp1860) + fbprop1860 + rail1860 + water1860 + as.factor(educ) + inc.cat  +religion +female + age + blkprop.z00 + log(medinc.z10) + w.unemp.rate2014 + log(wbincratio2014) + state.abb*as.factor(year))
context.int.form <- formula(. ~ pslave1860   + log(coarea00) + latitude + I(latitude^2) + longitude + I(longitude^2) + rugged + land.ineq1860 + sfarmprop1860 + log(totpop1860) + log(fvalpac1860) + log(acimp1860) + fbprop1860 + rail1860 + water1860 + as.factor(educ) +  inc.cat  +religion +female + age + blkprop.z00*pslave1860 + log(medinc.z10)*pslave1860 + w.unemp.rate2014*pslave1860 + log(wbincratio2014)*pslave1860 + state.abb*as.factor(year))

## have to use Formula package for ivreg calls
# ivreg: Instrumental-Variable Regression - estimate causal relationships when
# controlled experiments are not feasible
# Formula for looking at locational data
base.iv.form <- Formula(. ~ pslave1860 + log(coarea00) + rugged + latitude + I(latitude^2) + longitude + I(longitude^2)  + water1860  + state.abb | cottonsuit + log(coarea00) + rugged  + latitude + I(latitude^2) + longitude + I(longitude^2) + water1860  + state.abb)

# The not reduced form formula for the locational data
base.first.form <- formula(pslave1860 ~ cottonsuit + log(coarea00) + rugged + latitude + I(latitude^2) + longitude + I(longitude^2)  +water1860 + state.abb)

# Reduced form formula for the locational data - need to find out what that means in this context
rform.form <- formula(. ~  cottonsuit + log(coarea00) + rugged + latitude + I(latitude^2)+ longitude + I(longitude^2)  + water1860+  state.abb)
```
# Figure 2
```{r f2}
# Figure 2 
# Setting the parameters for the plots
par(mfrow = c(1,4), mar = 0.1 + c(4, 3, 2, 0.5), cex.main = 1)

# Plotting Proportion Slave, 1860 portion of the figure with x-axis having
# proportion of slaves and y-axis having proportion of democrats along with
# adding a line that correlates democrats with proportion of slaves in 1860
plot(south.counties$pslave1860, south.counties$dem, 
     pch = 19, col = "#33333333", xlab = "Proportion Slave, 1860", ylab = "", 
     main = "Proportion Democrat", yaxt = "n", cex = south.counties$sample.size/100)
axis(side = 2, las = 2)
abline(lm(dem ~ pslave1860, data = south.counties, weights = sample.size), lwd = 2, col = "#AA0000")

# Plotting Affirmative Action portion of the figure with x-axis having
# proportion of slaves and y-axis having proportion with approval of affirmative
# action along with adding a line that correlates affirmative action with
# proportion of slaves in 1860
plot(south.counties$pslave1860, south.counties$affirm, 
     pch = 19, col = "#33333333", xlab = "Proportion Slave, 1860", ylab = "", 
     main = "Affirmative Action", yaxt = "n", cex = south.counties$sample.size/100)
axis(side = 2, las = 2)
abline(lm(affirm ~ pslave1860, data = south.counties, weights = sample.size), lwd = 2, col = "#AA0000")

# Plotting Racial Resentment portion of the figure with x-axis having proportion
# of slaves and y-axis having proportion with racial resentment along with
# adding a line that correlates racial resentment with proportion of slaves in
# 1860
plot(south.counties$pslave1860, south.counties$resent, 
     pch = 19, col = "#33333333", xlab = "Proportion Slave, 1860", ylab="", 
     main = "Racial Resentment", yaxt = "n", cex = south.counties$sample.size.res/75)
axis(side = 2, las = 2)
abline(lm(resent ~ pslave1860, data = south.counties, weights = sample.size.res), lwd = 2, col = "#AA0000")

# Plotting Racial Thermometer portion of the figure with x-axis having
# proportion of slaves and y-axis having thermometer scores along with adding a
# line that correlates thermometer scores with proportion of slaves in 1860
with(subset(nes.counties, state.abb %in% st.list), 
     plot(pslave1860, wtherm-btherm, 
          cex = sample.size.bt/40, pch = 19, col = "#33333333", 
          xlab = "Proportion Slave, 1860", ylab = "", 
          main = "White - Black Therm. Score", las = 1, xlim = c(0, 0.9)))
abline(lm(I(wtherm-btherm) ~ pslave1860, weights = sample.size.bt, data = subset(nes.counties, state.abb %in% st.list)), lwd = 2, col = "#AA0000")
```

# Table 1
```{r t1, results = 'asis'}
# Using the formulas from above to create linear models used in the creation of
# Table 1 on the county level
cnty.res <- lm(dem ~ pslave1860, data = south.counties, weights = sample.size)
cnty.res.fe <- lm(dem ~ pslave1860 + state.abb, data = south.counties, weights = sample.size)
cnty.res.full <- lm(update(base1860.form, dem ~ .), data = south.counties, weights = sample.size)
cnty.aff <- lm(affirm ~ pslave1860, data = south.counties, weights = sample.size)
cnty.aff.fe <- lm(affirm ~ pslave1860 + state.abb, data = south.counties, weights = sample.size)
cnty.aff.full <- lm(update(base1860.form, affirm ~ .), data = south.counties, weights = sample.size)
cnty.resent <- lm(resent ~ pslave1860, data = south.counties, weights = sample.size.res)
cnty.resent.fe <- lm(resent ~ pslave1860 +  state.abb, data = south.counties, weights = sample.size.res)
cnty.resent.full <- lm(update(base1860.form, resent ~ .), data = south.counties, weights = sample.size.res)

## NES Individual Results
# Using the formulas from above to create linear models with standard errors used in the creation of
# Table 1 on the individual level
therm.mod <- lm(therm.diff ~ pslave1860, data = ns.whites, weights = weight)
therm.mod.rse <- robust.se(therm.mod, clvar = "fips")

therm.mod.fe <- lm(therm.diff ~ pslave1860 + state.abb*as.factor(year), data = ns.whites, weights = weight)
therm.mod.fe.rse <- robust.se(therm.mod.fe, clvar = "fips")

therm.1860 <- lm(update(base1860.form, therm.diff ~ . + state.abb*as.factor(year)), data = ns.whites, weights = weight)
therm.1860.rse <- robust.se(therm.1860, clvar = "fips")

# Outputs the complete table 1 with all of the models inputted from the 
# formulas above
tab1.alt <- stargazer(cnty.res, cnty.res.full, cnty.aff.full, cnty.resent.full, therm.1860,
                      se = list(NULL, NULL, NULL, NULL, therm.1860.rse[,2]),
                      keep = "pslave1860", style = "apsr", omit.stat = c("adj.rsq","ll", "F", "ser"),
                      covariate.labels = c("Prop. Slave, 1860"), 
                      dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"),
                      column.sep.width = "5pt", float = FALSE, header = FALSE, 
                      add.lines = list(rep("", 4), 
                                       c("Level", "County", "County", "County", "County", "Individual"),
                                       ch.row("1860 Covariates", c(FALSE, rep(TRUE,3), FALSE)), 
                                       ch.row("State Fixed Effects", c(FALSE, rep(TRUE,4))),
                                       ch.row("State-Year Fixed Effects", c(rep(FALSE,4), TRUE)),
                                       ch.row("Clustered SEs", c(rep(FALSE,4), TRUE)), rep("", 4)),
                      multicolumn = TRUE)
```
Note. Models 1–4 are weighted least squares at the county level, with within-county sample sizes, adjusted by sampling weights, as weights. Model 5 is weighted least squares at the individual level with state-year fixed effects. Standard errors, in parentheses, are clustered at the county level in model 5. There are 50 counties in model 5.

# Table 2
```{r t2, results = 'asis'}
## Neighbor matching
cnty.res.neighbor <- lm(update(base1860.form, dem ~ .),
                        data = south.counties, weights = sample.size, subset = nmatch.diff.20 == 1)
cnty.aff.neighbor <- lm(update(base1860.form, affirm ~ .), 
                        data = south.counties, weights = sample.size, subset = nmatch.diff.20 == 1)
cnty.resent.neighbor <- lm(update(base1860.form, resent ~ .), 
                           data = south.counties, weights = sample.size.res, subset = nmatch.diff.20 == 1)

## Matching (Non-slave south versus north)
## Note that there will be some slight deviation from the results in
## the paper due to the random nature of k2k matching in this context
mdata <- wh.counties[which(!(wh.counties$state.abb %in% st.list) | wh.counties$pslave < 0.05),]
mdata <- mdata[which(!(mdata$state.abb %in% c("MD", "DE"))), ]
mvars <- c("dem", "affirm", "resent","south", "fvalpc1860", 
           "fbprop1860", "totpop1860", "longitude", "latitude", "coarea00")
mdata$south <- 1 * (mdata$state.abb %in% st.list)
mout <- cem("south", data = mdata[,mvars], drop = c("dem", "affirm", "resent"), k2k = TRUE)

match.dem <- lm(update(base1860.form, dem ~ south + . - pslave1860 - state.abb), data = mdata, weights = sample.size, subset = mout$w > 0)

match.aff <- lm(update(base1860.form, affirm ~ south + . - pslave1860 - state.abb), data = mdata, weights = sample.size, subset = mout$w > 0)

match.resent <- lm(update(base1860.form, resent ~ south + . - pslave1860 - state.abb), data = mdata, weights = sample.size.res, subset = mout$w > 0)

match.tab <- stargazer(cnty.res.neighbor, match.dem, cnty.aff.neighbor, 
                       match.aff, cnty.resent.neighbor, match.resent,
                       dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"), 
                       keep = c("pslave1860","south"), 
                       covariate.labels = c("Prop. Slave, 1860","Slave State"),
                       style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"), 
                       column.sep.width = "0pt", float = FALSE, header = FALSE, 
                       add.lines = list(rep("", 7), ch.row("State Fixed Effects", rep(c(TRUE,FALSE),3)),
                                        ch.row("1860 Covariates", rep(TRUE, 6)), 
                                        ch.row("50\\% Threshold Match", rep(c(TRUE,FALSE), 3)),
                                        ch.row("North-South Match", rep(c(FALSE,TRUE), 3)), 
                                        rep("", 7)), 
                       multicolumn = TRUE)

```
# Table 3
```{r t3, results = 'asis'}
cnty.res.blk70.ptbias <- lm(update(base1860.form, dem ~ . + blkprop70), 
                            data =south.counties, weights = sample.size)
cnty.res.blk00.ptbias <- lm(update(base1860.form, dem ~ . + blkprop00), 
                            data =south.counties, weights = sample.size)
cnty.aff.blk70.ptbias <- lm(update(base1860.form, affirm ~ . + blkprop70), 
                            data = south.counties, weights = sample.size)
cnty.aff.blk00.ptbias <- lm(update(base1860.form, affirm ~ . + blkprop00), 
                            data = south.counties, weights = sample.size)
cnty.resent.blk70.ptbias <- lm(update(base1860.form, resent ~ . + blkprop70), 
                               data = south.counties, weights = sample.size.res)
cnty.resent.blk00.ptbias <- lm(update(base1860.form, resent ~ . + blkprop00), 
                               data = south.counties, weights = sample.size.res)
cnty.dem.blk00.first <- lm(update(base1860.form, dem ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =south.counties, weights = sample.size)
cnty.dem.blk00.iv <- ivreg(update(base.iv.form, I(dem - coef(cnty.dem.blk00.first)["blkprop00"]*blkprop00) ~ .), data = south.counties, weights = sample.size)
cnty.dem.blk00 <- lm(update(base1860.form, I(dem - coef(cnty.dem.blk00.first)["blkprop00"]*(blkprop00)) ~ .), data =south.counties, weights = sample.size)
cnty.aff.blk00.first <- lm(update(base1860.form, affirm ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =south.counties, weights = sample.size)
cnty.aff.blk00.iv <- ivreg(update(base.iv.form, I(affirm - coef(cnty.aff.blk00.first)["blkprop00"]*blkprop00) ~ .), data = south.counties, weights = sample.size)
cnty.aff.blk00 <- lm(update(base1860.form, I(affirm - coef(cnty.aff.blk00.first)["blkprop00"]*(blkprop00)) ~ .), data =south.counties, weights = sample.size)
cnty.resent.blk00.first <- lm(update(base1860.form, resent ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =south.counties, weights = sample.size.res)
cnty.resent.blk00.iv <- ivreg(update(base.iv.form, I(resent - coef(cnty.resent.blk00.first)["blkprop00"]*blkprop00) ~ .), data = south.counties, weights = sample.size.res)
cnty.resent.blk00 <- lm(update(base1860.form, I(resent - coef(cnty.resent.blk00.first)["blkprop00"]*(blkprop00)) ~ .), data =south.counties, weights = sample.size.res)

## bootstrap the SEs
set.seed(6251983)
boots <- 1000
cnty.dem.blk00.boots <- rep(NA, times = boots)
cnty.aff.blk00.boots <- rep(NA, times = boots)
cnty.resent.blk00.boots <- rep(NA, times = boots)
for (b in 1:boots) {
  sc.star <- south.counties[sample(1:nrow(south.counties), replace = TRUE),]
  boot.dem.first <- lm(update(base1860.form, dem ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =sc.star, weights = sample.size)
  boot.dem  <- lm(update(base1860.form, I(dem - coef(boot.dem.first)["blkprop00"]*(blkprop00)) ~ .), 
                  data =sc.star, weights = sample.size)
  cnty.dem.blk00.boots[b] <- coef(boot.dem)["pslave1860"]

  boot.aff.first <- lm(update(base1860.form, affirm ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =sc.star, weights = sample.size)
  boot.aff  <- lm(update(base1860.form, I(affirm - coef(boot.aff.first)["blkprop00"]*(blkprop00)) ~ .), 
                  data =sc.star, weights = sample.size)
  cnty.aff.blk00.boots[b] <- coef(boot.aff)["pslave1860"]

  boot.resent.first <- lm(update(base1860.form, resent ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =sc.star, weights = sample.size.res)
  boot.resent <- lm(update(base1860.form, I(resent - coef(boot.resent.first)["blkprop00"]*(blkprop00)) ~ .),
                    data =sc.star, weights = sample.size.res)
  cnty.resent.blk00.boots[b] <- coef(boot.resent)["pslave1860"]
}

# Put bootstrapped SEs into a holder (we don't calculate the BSE for
# the other coefficients since we don't care about them and don't
# report them in the paper)
dem.bse <- summary(cnty.dem.blk00)$coef[,2]
dem.bse["pslave1860"] <- sd(cnty.dem.blk00.boots)
aff.bse <- summary(cnty.aff.blk00)$coef[,2]
aff.bse["pslave1860"] <- sd(cnty.aff.blk00.boots)
resent.bse <- summary(cnty.resent.blk00)$coef[,2]
resent.bse["pslave1860"] <- sd(cnty.resent.blk00.boots)

blkprop.tab <- stargazer(cnty.res.blk00.ptbias, cnty.dem.blk00, cnty.aff.blk00.ptbias, cnty.aff.blk00, cnty.resent.blk00.ptbias, cnty.resent.blk00,
          keep = c("pslave1860", "blkprop00"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"), se = list(NULL, dem.bse, NULL, aff.bse, NULL, resent.bse),
          covariate.labels = c("Prop. Slave, Direct Effect", "Prop. Black, 2000"), 
          dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"), 
          column.sep.width = "5pt", float = FALSE, header = FALSE, 
          add.lines = list(rep("", 7), ch.row("State Fixed Effects", rep(TRUE, 6)), 
                           ch.row("1860 Covariates", rep(TRUE, 6)), 
                           ch.row("Bootstrapped SEs", rep(c(FALSE,TRUE), 3)), 
                           c("Model", rep(c("WLS", "Seq. g-est."), 3)), rep("", 7)), 
          multicolumn = TRUE)
```
Note. Columns 1, 3, and 5 simply include proportion black in the year 2000 as an additional control to the baseline specification from table 1. Columns 2, 4, and 6 use sequential g-estimation (Seq, g-est) of Vansteelandt (2009). WLS p weighted least squares. Standard errors are in parentheses.

```{r}

# ## Appendix Table
# seqg.tab <- stargazer(cnty.dem.blk00.first, cnty.aff.blk00.first, cnty.resent.blk00.first,
#                       keep = c("pslave1860", "blkprop00", "totpop00", "highsch90",
#                                "unemp","medinc","wbincratio"), 
#                       style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
#                       covariate.labels = c("Prop. Slave, 1860","Prop. Black 2000", "Log Population, 2000",
#                                            "Percent High School Graduates, 1990", "Unemployment, 1999", 
#                                            "Median Income, 2000", "White-Black Income Ratio, 2000"),
#                       dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"),
#                       column.sep.width = "5pt", float = FALSE, header = FALSE, 
#                       add.lines = list(rep("", 4), ch.row("State Fixed Effects", rep(TRUE, 3)), 
#                                        ch.row("1860 Covariates", rep(TRUE, 3)), rep("", 4)), 
#                       multicolumn = FALSE)
# 
# ## antebellum results
# cnty.dem.houses <- lm(update(base1860.form, dem ~ . + slavesperhouse), 
#                       data = south.counties, weights = sample.size)
# cnty.aff.houses <- lm(update(base1860.form, affirm ~ . + slavesperhouse), 
#                       data = south.counties, weights = sample.size)
# cnty.resent.houses <- lm(update(base1860.form, resent ~ . + slavesperhouse), 
#                          data = south.counties, weights = sample.size.res)
# cnty.dem.mortrate <- lm(update(base1860.form, dem ~ . + I(log(s.mortrate/w.mortrate))), 
#                         data = south.counties, weights = sample.size, subset = s.mortrate > 0)
# cnty.aff.mortrate <- lm(update(base1860.form, affirm ~ . + I(log(s.mortrate/w.mortrate))), 
#                         data = south.counties, weights = sample.size, subset = s.mortrate > 0)
# cnty.resent.mortrate <- lm(update(base1860.form, resent ~ . + I(log(s.mortrate/w.mortrate))), 
#                            data = south.counties, weights = sample.size.res, subset = s.mortrate > 0)
# 
# ante.tab <- stargazer(cnty.dem.mortrate, cnty.dem.houses, cnty.aff.mortrate, 
#                       cnty.aff.houses, cnty.resent.mortrate, cnty.resent.houses,
#                       keep = c("pslave1860", "mortrate", "slavesperhouse"), 
#                       style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
#                       covariate.labels = c("Prop. Slave, 1860", "Log Relative Slave Mortality, 1860", 
#                                            "Avg. Residents per Slave Dwelling"), 
#                       dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"),
#                       column.sep.width = "5pt", float = FALSE, header = FALSE, 
#                       add.lines = list(rep("", 7), ch.row("State Fixed Effects", rep(TRUE, 6)), 
#                                        ch.row("1860 Covariates", rep(TRUE, 6)), rep("", 7)), 
#                       multicolumn = FALSE)

# ## 1851 Gubernatorial elections in MS and GA
# ## see txt files accompanying these csv files for codebooks
# ## Data comes from ICPSR 00001
# 
# ga.votes <- read.csv("dataverse_files/ga-votes-1824-1860.csv", stringsAsFactors = FALSE)
# ga.votes$cfips <- strtrim(ga.votes$V3, nchar(ga.votes$V3)-1)
# ga.votes$fips <- as.numeric(paste(13, str_pad(ga.votes$cfips, 3, side = "left", pad = "0"), sep = ""))
# is.na(ga.votes) <- ga.votes == 9999999
# ga.votes$howell1851 <- ga.votes$V345/ga.votes$V348
# 
# 
# ga.votes <- merge(ga.votes, countydata, by = "fips", all.x = TRUE, all.y = FALSE)
# 
# 
# lattice::xyplot(howell1851 ~ sprop1850, data = ga.votes, subset = state.abb %in% st.list , pch = 16, lwd = 4, col.line = "indianred", col = dodgerblue.30, xlab = "Proportion Slave, 1850", ylab = "Howell Cobb Vote-share, 1851", panel =
#                     function(x,y,...) {  panel.xyplot(x, y, ...)
#                                          panel.smoother(x,y,method = "loess", col = "indianred", lwd = 4)})
# 
# 
# ms.votes <- read.csv("dataverse_files/ms-votes-1824-1860.csv", stringsAsFactors = FALSE)
# ms.votes$cfips <- strtrim(ms.votes$V3, nchar(ms.votes$V3)-1)
# ms.votes$fips <- as.numeric(paste(28, str_pad(ms.votes$cfips, 3, side = "left", pad = "0"), sep = ""))
# is.na(ms.votes) <- ms.votes == 9999999
# ms.votes$foote1851 <- ms.votes$V187/ms.votes$V190
# 
# ms.votes <- merge(ms.votes, countydata, by = "fips", all.x = TRUE, all.y = FALSE)
# 
# 
# lattice::xyplot(foote1851 ~ sprop1850, data = ms.votes, subset = state.abb %in% st.list , pch = 16, lwd = 4, col.line = "indianred", col = dodgerblue.30, xlab = "Proportion Slave, 1850", ylab = "Henry Foote Vote-share, 1851", panel =
#                     function(x,y,...) {  panel.xyplot(x, y, ...)
#                                          panel.smoother(x,y,method = "loess", col = "indianred", lwd = 4)})
# 
# 
# #cairo_pdf(filename = "figs/ms-ga-1851-vote.pdf", family = "Minion Pro", height = 4.5, width = 9, pointsize = 11)
# p1 <- lattice::xyplot(howell1851 ~ sprop1850, data = ga.votes, subset = state.abb %in% st.list , pch = 16, lwd = 4, ylim = c(0,1), col.line = "indianred", main = "Georgia Gubernatorial Election, 1851", col = dodgerblue.30, xlab = "Proportion Slave, 1850", ylab = "Howell Cobb Vote-share, 1851", panel =
#                     function(x,y,...) {  panel.xyplot(x, y, ...)
#                                          panel.smoother(x,y,method = "loess", col = "indianred", lwd = 4)})
# p2 <- lattice::xyplot(foote1851 ~ sprop1850, data = ms.votes, subset = state.abb %in% st.list , pch = 16, lwd = 4, ylim = c(0,1), col.line = "indianred", main = "Mississippi Gubernatorial Election, 1851", col = dodgerblue.30, xlab = "Proportion Slave, 1850", ylab = "Henry Foote Vote-share, 1851", panel =
#                     function(x,y,...) {  panel.xyplot(x, y, ...)
#                                          panel.smoother(x,y,method = "loess", col = "indianred", lwd = 4)})
# plot(p1, position = c(0.0, 0, 0.49, 1), more = TRUE)
# plot(p2, position = c(0.5, 0, 1, 1))
```









